literature coding explore

### 2024-02-03 docs/lit_codes_explore.qmd
study info figures added to lit explore doc

@@

@@

@@

#### Conservation problem being addressed
:::

>>>>

```{r}
#| include: false
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
library(tidyquant)
library(here)

codes_vars <- read.csv(here("data/code_w_vars.csv"))
code_freq <- read.csv(here("data/code_freq2.csv"))
keywords <- read.csv(here("data/keywords.csv"))
occur_all <- read.csv(here("data/overlap_all.csv"))
occur_br <- read.csv(here("data/overlap_bridge.csv"))
occur_ba <- read.csv(here("data/overlap_barrier.csv"))
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 7

codes_vars$broad_location <- as.factor(codes_vars$broad_location)
codes_LU <- codes_vars[!duplicated(codes_vars$Lit_unit), ]
reg_s <- codes_LU %>%
  group_by(broad_location) %>%
  filter(broad_location != "NA" & broad_location != "Europe and United States") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

reg_bar <- ggplot(reg_s) +
  geom_bar(aes(x = perc, y = reorder(broad_location, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 48))+
  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
  geom_text(aes(x = perc, y = broad_location, label = broad_location),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Econ Sans Cnd",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Econ Sans Cnd",
      size = 13)
  )

reg_bar
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 10
#| fig-width: 10
fsh_shp <- codes_LU %>%
  gather(col, fsh_shp, fishery_or_channel1:fishery_or_channel4) %>%
  subset(select = fsh_shp)

fsh_shp_s <- fsh_shp %>%
  group_by(fsh_shp) %>%
  filter(fsh_shp != "NA") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

fsh_shp_bar <- ggplot(fsh_shp_s) +
  geom_bar(aes(x = perc, y = reorder(fsh_shp, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 14))+
  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Econ Sans Cnd", size = 15)) + 
  geom_text(aes(x = perc, y = fsh_shp, label = fsh_shp),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Econ Sans Cnd",
    size = 5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Econ Sans Cnd",
      size = 16)
  )

fsh_shp_bar
```

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 7

species <- codes_LU %>%
  gather(col, taxa, focal_taxa1:focal_taxa3) %>%
  subset(select = taxa)

spp_s <- species %>%
  group_by(taxa) %>%
  filter(taxa != "NA" & taxa != "Marine mammals") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

taxa_bar <- ggplot(spp_s) +
  geom_bar(aes(x = perc, y = reorder(taxa, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 23))+
  scale_y_discrete(expand = expansion(add = c(0.5,0.5))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
  geom_text(aes(x = perc, y = taxa, label = taxa),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Econ Sans Cnd",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Econ Sans Cnd",
      size = 13)
  )

taxa_bar
```

#### Conservation problem being addressed

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 7
#| fig-height: 7

consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  subset(select = consv_topic)

consv_s <- consv %>%
  group_by(consv_topic) %>%
  filter(consv_topic != "NA") %>%
  summarise(count = n()) %>%
  ungroup() %>%
  mutate(perc = count/sum(count)*100)

consv_bar <- ggplot(consv_s) +
  geom_bar(aes(x = perc, y = reorder(consv_topic, perc)), fill = "dodgerblue4", width = 0.6, stat = "identity")+
  scale_x_continuous(position = "top", 
                     expand = c(0,0), 
                     limits = c(0, 18))+
  scale_y_discrete(expand = expansion(add = c(0,0))) + 
  theme(
    # Set background color to white
    panel.background = element_rect(fill = "white"),
    # Set the color and the width of the grid lines for the horizontal axis
    panel.grid.major.x = element_line(color = "#A8BAC4", size = 0.3),
    # Remove tick marks by setting their length to 0
    axis.ticks.length = unit(0, "mm"),
    # Remove the title for both axes
    axis.title = element_blank(),
    # Only left line of the vertical axis is painted in black
    axis.line.y.left = element_line(color = "black"),
    # Remove labels from the vertical axis
    axis.text.y = element_blank(),
    # But customize labels for the horizontal axis
    axis.text.x = element_text(family = "Econ Sans Cnd", size = 12)) + 
  geom_text(aes(x = perc, y = consv_topic, label = consv_topic),
    hjust = 0,
    nudge_x = 0.3,
    colour = "dodgerblue4",
    family = "Econ Sans Cnd",
    size = 3.5)+
  labs(subtitle = "Percent of sum from all articles (%)") + 
  theme(plot.subtitle = element_text(
      family = "Econ Sans Cnd",
      size = 13)
  )

consv_bar
```
:::
